ediblecity: an R package to model and estimate the benefits of urban agriculture

### 2023-09-15 paper_v01.Rmd
submit version 02

# map(scenarios, ~ UHI(.x, SVF = ediblecity::SVF, return_raster = TRUE), .id = "Scenarios") |>
#   map(~ ggplot()+
#         stars::geom_stars(data = .x, na.action = na.omit)+
#         coord_equal()+
#         scale_fill_distiller(palette = "RdYlBu")+
#         theme_void()+
#         theme(plot.title = element_text(hjust=0.5))
#       ) |>
#   map2(names(scenarios), ~ .x+labs(title = .y)) |>
#   wrap_plots()+plot_layout(guides = 'auto', nrow = 1)
# 
# ggsave("assets/UHI_plots.png")

>>>>

map(scenarios, ~ UHI(.x, SVF = ediblecity::SVF, return_raster = TRUE), .id = "Scenarios") |>
  map(~ ggplot()+
        stars::geom_stars(data = .x, na.action = na.omit)+
        coord_equal()+
        scale_fill_distiller(palette = "RdYlBu")+
        theme_void()+
        theme(plot.title = element_text(hjust=0.5))
      ) |>
  map2(names(scenarios), ~ .x+labs(title = .y)) |>
  wrap_plots()+plot_layout(guides = 'auto', nrow = 1)

ggsave("assets/UHI_plots.png")
